---
title: "testpack description"
author: "F. Max"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{testpack description}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    library(testpack),
    collapse = TRUE,
    comment = "#>"
)
df <- fars.test.df
```

`testpack` is meant for loading and visualizing data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System. The following functions are contained:

- **`make_filename`** generates a string according to the format of FARS dataset file names, mainly adopted for internal use
- **`fars_read`** loads a full dataset from file. An appropriate file name must be provided in input
- **`fars_read_years`** loads the `MONTH` and `year` columns of all the accidents occurred in the years provided in input
- **`fars_summarize_years`** produces a data frame summarizing the number of accidents per month for each year provided in input
- **`fars_map_state`** draws a map with marks representing the geographic locations of the occurrence of the accidents, for the year and the state provided in input

## `testpack` at work

**`make_filename`** is internally used to generate appropriate FARS data file names. Appropriate input is expected in order to generate meaningful file names.
```{r}
make_filename(2013)
make_filename("2015")
make_filename(3.14159)
```
***
**`fars_read`** loads a full dataset from an appropirate FARS file.

```{r, eval=FALSE}
df <- fars_read(2018)
```

The data frame should look like this:
```{r}
head(df, 7)
```

***
**`fars_read_years`** loads the `MONTH` and `year` columns of all the accidents occurred in the years provided in input

```{r, eval=FALSE}
df <- fars_read(2018)
```

The data frame should look like this:
```{r echo=FALSE}
df1 <- dplyr::select(df, MONTH, YEAR)
```
```{r}
head(df1, 9)
```
***
**`fars_summarize_years`** produces a data frame summarizing the number of accidents per month for each year provided in input

```{r, eval=FALSE}
df <- fars_read_years( c(2013, 2018) )
```

***
**`fars_map_state`** draws a map with marks representing the geographic locations of the occurrence of the accidents, for the year and the state provided in input

## Additional info

Check out also the the help of the functions for additional details. The package comes along with a data frame `fars.data.df`, obtained randomly sampling 1,000 entries of the FARS data of year 2013.
